---
title: "R Notebook"
output: html_notebook
---
1. Preprocessing 
 check missing values
 check data types
 *extract categorical columns from some continous variables (CTR, Conversion Rate) if distribution is skewed
 
2. EDA 
 summary statistics for numerical variables
 visualize distribution of key metrics (CTR, Conversion Rate, Bounce Rate, Scroll Depth, Session Duration)
 Examine categorical variable distributions (Purchases , added to cart, location)
 check outliers in numerical columns
 
2. Visualizations
 Compare proportions of purchases, added to cart, and categorized columns - bar chart
 Visualize distribution of Scroll Depth, Session duration by theme - boxplot
 density distribution of numerical variables - histogram and KDE plots
 
4. Hypothesis Testing 
 2-sample proportion for binary categorical variables (purchases, added to cart, *CTR, *conversion rate)
 t-test or mann-whitney u for continuous variables  (scroll depth, session duration)
 
 









```{r}
library(tidyverse)
library(skimr)
library(ggExtra)
```


```{r}
data <- read_csv('website_ab_test.csv')
```


```{r}
glimpse(data)
skim(data)
```


```{r}
#rename numerical columns
names <- c(Click_Through_Rate = 'Click Through Rate', Conversion_Rate = 'Conversion Rate', Bounce_Rate = 'Bounce Rate')
data <- data %>% rename(all_of(names))

#change character columns to factor
data[, sapply(data, is.character)] <- lapply(data[, sapply(data, is.character)], as.factor)
```


```{r}

```

```{r}

```


```{r}
# Define a color palette
palette <- c("#1b9e77", "#d95f02") # Adjust colors as needed

data %>%
  ggplot(aes(Click_Through_Rate, fill = Theme)) +
  geom_histogram(color = 'black', bins = 30, alpha = 0.7, position = "dodge") +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Click Through Rate Distribution", x = "CTR", y = "Frequency") +
   theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13))

data %>%
  ggplot(aes(Conversion_Rate, fill = Theme)) +
  geom_histogram(color = 'black', bins = 30, alpha = 0.7, position = "dodge") +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Conversion Rate Distribution", x = "Conversion Rate", y = "Frequency") +
   theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13))

data %>%
  ggplot(aes(Bounce_Rate, fill = Theme)) +
  geom_histogram(color = 'black', bins = 30, alpha = 0.7, position = "dodge") +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Bounce Rate Distribution", x = "Bounce Rate", y = "Frequency") +
   theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13))


data %>%
  ggplot(aes(Scroll_Depth, fill = Theme)) +
  geom_histogram(color = 'black', bins = 30, alpha = 0.7, position = "dodge") +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Scroll Depth Distribution", x = "Scroll Depth", y = "Frequency") +
   theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13))

data %>%
  ggplot(aes(Session_Duration, fill = Theme)) +
  geom_histogram(color = 'black', bins = 30, alpha = 0.7, position = "dodge") +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Session Duration Distribution", x = "Session Duration", y = "Frequency") +
   theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13))

# Arrange plots in a 2-column layout for better visualization
#grid.arrange(ctr_histo, cr_histo, br_histo, sd_histo, ssd_histo, ncol = 2)
```








```{r}

#Boxplot for Session Duration
ggplot(data, aes(Theme, Session_Duration, fill = Theme)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Session Duration by Theme", x = "Theme", y = "Session Duration") +
   theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13))

#Boxplot for Scroll Depth
ggplot(data, aes(Theme, Scroll_Depth, fill = Theme)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Scroll Depth by Theme", x = "Theme", y = "Scroll Depth") +
  theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13 ))


#Boxplot for Conversion Rate

ggplot(data, aes(Theme, Conversion_Rate, fill = Theme)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  scale_fill_manual(values = palette) +
  theme_minimal() +
  labs(title = "Conversion Rate by Theme", x = "Theme", y = "Conversion Rate") +
  theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.4, vjust = 0.9,       # this Centers the title
                     margin = margin(t = 2, b = 15)), 
        axis.title.x = element_text(
                       size = 13
                       ),
        axis.title.y = element_text(
                       size = 13 ))
```





```{r}
# Bar plot for Purchases by Theme
data %>%  ggplot(aes(Purchases, fill = Theme)) +
  geom_bar(position = "dodge", width = 0.7, alpha = 0.7) +
  scale_fill_manual(values = palette) +
  labs(title = "NUMBER OF PURCHASES BY THEME", x = "Purchases") +
  geom_text(
           stat = "count", 
           aes(label = after_stat(count)),
           position = position_dodge(width = 0.7),
           vjust = -0.5) +
  theme_minimal() +
  theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.7, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 10)), 
        axis.title.x = element_text(
                       size = 13,
                       ),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(), #removes y axis properties
        axis.title.y = element_blank(), 
        panel.grid = element_blank())

# Bar plot for Added to Cart
data %>%  ggplot(aes(Added_to_Cart, fill = Theme)) +
  scale_fill_manual(values = palette) +
  geom_bar(position = "dodge", width = 0.7, alpha = 0.7) +
  labs(title = "NUMBER OF CARTS ADDITION BY THEME",x = "Added to Cart") +
  geom_text(
           stat = "count", 
           aes(label = after_stat(count)),
           position = position_dodge(width = 0.7),
           vjust = -0.5) +
  theme_minimal() +
  theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.7, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 10)), 
        axis.title.x = element_text(
                       size = 13,
                       ),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank(), 
        panel.grid = element_blank())
```

```{r}
data %>%  ggplot(aes(Location, fill = Theme)) +
  scale_fill_manual(values = palette) +
  geom_bar(position = "dodge", width = 0.7, alpha = 0.7) +
  labs(title = "USER LOCATION BY THEME",x = "Location") +
  geom_text(
           stat = "count", 
           aes(label = after_stat(count)),
           position = position_dodge(width = 0.7),
           vjust = -0.5) +
  theme_minimal() +
  theme(plot.title = element_text(
                     size = 16,
                     face = "bold",
                     color = "black",
                     hjust = 0.7, vjust = 0.9,       # this Center the title
                     margin = margin(t = 2, b = 10)), #Set the margin of title
        axis.title.x = element_text(
                       size = 13,
                       ),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank(), 
        panel.grid = element_blank())
```


STATISTICAL TESTS

```{r}
light_theme_data <- data %>%  filter(Theme == 'Light Theme')
dark_theme_data <- data %>%  filter(Theme == 'Dark Theme')
```

```{r}
#check 2-sample proportion test for purchases 
prop_dark_purchase = dark_theme_data %>%  
            filter(Purchases == 'Yes') %>%  
            nrow()
n_dark_purchase = nrow(dark_theme_data)

prop_light_purchase = light_theme_data %>%
             filter(Purchases == 'Yes') %>%
             nrow()
n_light_purchase =  nrow(light_theme_data)

purchase_test <- prop.test(x = c(prop_dark_purchase, prop_light_purchase), n = c(n_dark_purchase, n_light_purchase), correct = FALSE)
```

```{r}
#check 2-sample proportion test for added to cart
prop_dark_cart = dark_theme_data %>%  
            filter(Added_to_Cart == 'Yes') %>%  
            nrow()
n_dark_cart = nrow(dark_theme_data)

prop_light_cart = light_theme_data %>%
             filter(Added_to_Cart == 'Yes') %>%
             nrow()
n_light_cart =  nrow(light_theme_data)

cart_test <- prop.test(x = c(prop_dark_cart, prop_light_cart), n = c(n_dark_cart, n_light_cart), correct = FALSE)
```


```{r}
purchase_test
cart_test
```


TEST FOR NORMALITY FOR SESSION DURATION AND SCROLL DEPTH

```{r}
normality_test <- function(x) {
  result <- shapiro.test(x)
  tidy_result <- broom::tidy(result)
  return(paste("The shapiro test p-value of", deparse(substitute(x)), "is", tidy_result$p.value))
}

check_qqplot <- function(x) {
   qqnorm(x, ,main = NULL)
   qqline(x, col = "red")
   title(main = deparse(substitute(x)))
 }

```





```{r}
#shapiro-wilk test for normality
normality_test(dark_theme_data$Scroll_Depth)
normality_test(dark_theme_data$Click_Through_Rate)
normality_test(dark_theme_data$Conversion_Rate)
normality_test(dark_theme_data$Bounce_Rate)
normality_test(dark_theme_data$Session_Duration)
normality_test(light_theme_data$Scroll_Depth)
normality_test(light_theme_data$Click_Through_Rate)
normality_test(light_theme_data$Conversion_Rate)
normality_test(light_theme_data$Bounce_Rate)
normality_test(light_theme_data$Session_Duration)

```

```{r}
#Q-Q plot check for normality
check_qqplot(dark_theme_data$Scroll_Depth)
check_qqplot(dark_theme_data$Click_Through_Rate)
check_qqplot(dark_theme_data$Conversion_Rate)
check_qqplot(dark_theme_data$Bounce_Rate)
check_qqplot(dark_theme_data$Session_Duration)
check_qqplot(light_theme_data$Scroll_Depth)
check_qqplot(light_theme_data$Click_Through_Rate)
check_qqplot(light_theme_data$Conversion_Rate)
check_qqplot(light_theme_data$Bounce_Rate)
check_qqplot(light_theme_data$Session_Duration)

```

```{r}
#wilcoxon test
wilcox.test(light_theme_data$Session_Duration, dark_theme_data$Session_Duration, correct = TRUE)
wilcox.test(light_theme_data$Scroll_Depth, dark_theme_data$Scroll_Depth,correct = FALSE)
```

```{r}

```


```{r}


```






```{r}

```

